\documentclass[12pt]{article} % use larger type; default would be 10pt
\usepackage[margin=1in]{geometry} % to change the page dimensions
         % otherwise the current date is printed 
%\usepackage{times}
\usepackage{times}
\usepackage{fancyhdr}
\usepackage{xspace}
\usepackage{hyperref}
\setlength\itemsep{0.2em}
\renewcommand\labelitemi{{\boldmath$\cdot$}}


\pagestyle{fancy}
\lhead{Studio-based HCI at Scale: CS160 Course Development Brief}
\rhead{\thepage}
%\cfoot{}

\begin{document}
\special{papersize=8.5in,11in}
\setlength{\pdfpageheight}{\paperheight}
\setlength{\pdfpagewidth}{\paperwidth}
\setlength{\parindent}{0pt} %Remove indent of all but first paragraph
\setlength{\parskip}{2ex} %Add space between paragraphs



\section{Project overview}
CS160 is expanding by 2X. This means we need new ways of submitting, grading, and tracking student progress. 
Salary: 4-5K.

In a nutshell: Collecting, sharing, critiquing project based materials. 




\subsection{Review}

\begin{itemize}
\item Review existing resources. 
\item \href{https://www.eecs.berkeley.edu/Students/gsi-resources.shtml}{EECS GSI Resources}
\end{itemize}

\subsection{Submission}
\begin{itemize}
\item Interface with Campus Authentication
\item Check into Github.
\item Design-log. 
\item Tagging. 
\end{itemize}

\subsection{Grading}
\begin{itemize}
\item Peer review. Assign to n-people; get critique.
\item Grading criteria (spotcheck)($>$ Tweet patterns.)
\item Plagiarism check (reverse image lookup)
\item Interface with Gradebook (participation)
\end{itemize}

\subsection{Tracking}
\begin{itemize}
\item Mailing mechanism on groups.
\item Assigning rooms to people (based on grades).
\item Team evaluation
\item Generate mailers (flag meeting with people)
\item Mailing mechanism on groups
\item Group assignment 
\item Shuffle dynamics
\end{itemize}

\subsection{Publicity}
\begin{itemize}
\item Select materials for hero-page. 
\item Public portfolio, archive
\end{itemize}

\section{Important Links}
\begin{itemize}
\item \href{https://github.com/cs160-fall2015/course-development}{GitHub Repo}
\end{itemize}
\section{Important Dates}
\begin{itemize}
\item \textbf{Fall Semester Begins} -- Wednesday, August 19 2015
\item \textbf{Instruction Begins} -- Wednesday, August 26 2015
\end{itemize}


\section{Contact}
\begin{itemize}
	\item Eric Paulos paulos@berkeley.com
	\item Cesar Torres cearto@berkeley.com  915-208-4709
	\item James Pierce pierjam@gmail.com
\end{itemize}

\end{document}
